### 2021-07-27 paper/paper.tex
update TODO note
update Trixi version after merging Jesse's PR

As of version v0.3.47 (July 2021), \trixi comes with the following features.
\begin{itemize}
  \item 1D, 2D, and 3D simulations on line/quad/hex meshes
  \begin{itemize}
    \item Cartesian and curvilinear meshes
    \item Conforming and non-conforming meshes
    \item Structured and unstructured meshes
    \item Hierarchical quadtree/octree grid with adaptive refinement
  \end{itemize}

  \item High-order nodal discontinuous Galerkin methods
  \begin{itemize}
    \item Kinetic energy preserving and entropy-stable methods
    \item Entropy-stable shock-capturing
    \item Positivity-preserving limiting
  \end{itemize}

@@

In traditional monolithic code bases, it is often necessary to implement a new
feature for all combinations of possible (compile time) options. This effort
can make it hard to experiment with new ideas. In contrast, Julia's dynamic
nature and just-ahead-of-time compiler allow us to implement only the features
that are strictly necessary. For example, if a user wants to simulate a new
physics model only on Cartesian grids with smooth solutions, there is no need
to implement anything for curvilinear coordinates or shock capturing approaches.
In addition, it allows to extend \trixi step by step with new capabilities.
For example, there are ongoing efforts to incorporate summation by parts finite
difference methods via SummationByPartsOperators.jl \cite{ranocha2021sbp} and
discontinuous Galerkin methods on simplices via StartUpDG.jl\footnote{\url{https://github.com/jlchan/StartUpDG.jl}} in \trixi. This becomes feasible since not every
feature combination needs to be considered and it is totally fine to start with
simple variants on a subset of the available meshes.

@@

\todo{ % TODO
\begin{itemize}
  \item Full paper: 5--10 pages
  \item Prepare repro repo including scripts for \trixi and Fluxo
  \item The title of our talk at JuliaCon is
  ``Adaptive and extendable numerical simulations with Trixi.jl''.
  Shall we use something like
  ``Adaptive high-order numerical simulations of hyperbolic PDEs with Trixi.jl:
  A case study of Julia for scientific computing'' for this paper?
  \item Restructure non-conservative stuff and add MHD benchmarks?
  \item Shall we re-create the schematic overview in tikz?
  \item Shall we compare \trixi to other open source frameworks such as MFEM, NGSolve, DealII, DUNE, FENICS, Firedrake, ClawPack, ...?
  \item Are there other aspects we should discuss?
\end{itemize}
\begin{quote}
  Compared to an extended abstract, a full paper presents more of the background
  and context motivating the work. It compares the work to other approaches taken
  in the field and gives some additional insights on the conference contribution.
  Use cases back up the work by showing how it can be used.
\end{quote}}

>>>>

% TODO: Update Trixi version
As of version v0.3.50 (July 2021), \trixi comes with the following features.
\begin{itemize}
  \item 1D, 2D, and 3D simulations on line/quad/hex/simplex meshes
  \begin{itemize}
    \item Cartesian and curvilinear meshes
    \item Conforming and non-conforming meshes
    \item Structured and unstructured meshes
    \item Hierarchical quadtree/octree grid with adaptive refinement
  \end{itemize}

  \item High-order nodal and modal discontinuous Galerkin methods
  \begin{itemize}
    \item Kinetic energy preserving and entropy-stable methods
    \item Entropy-stable shock-capturing
    \item Positivity-preserving limiting
  \end{itemize}

@@

In traditional monolithic code bases, it is often necessary to implement a new
feature for all combinations of possible (compile time) options. This effort
can make it hard to experiment with new ideas. In contrast, Julia's dynamic
nature and just-ahead-of-time compiler allow us to implement only the features
that are strictly necessary. For example, if a user wants to simulate a new
physics model only on Cartesian grids with smooth solutions, there is no need
to implement anything for curvilinear coordinates or shock capturing approaches.
In addition, it allows to extend \trixi step by step with new capabilities.
For example, there are ongoing efforts to incorporate summation by parts finite
difference methods via SummationByPartsOperators.jl \cite{ranocha2021sbp} and
more discontinuous Galerkin methods on simplices via StartUpDG.jl\footnote{\url{https://github.com/jlchan/StartUpDG.jl}} in \trixi. This becomes feasible since not every
feature combination needs to be considered and it is totally fine to start with
simple variants on a subset of the available meshes.

@@

\todo{ % TODO
\begin{itemize}
  \item Full paper: 5--10 pages
  \item Prepare repro repo including scripts for \trixi and Fluxo
  \item The title of our talk at JuliaCon is
  ``Adaptive and extendable numerical simulations with Trixi.jl''.
  Shall we use something like
  ``Adaptive high-order numerical simulations of hyperbolic PDEs with Trixi.jl:
  A case study of Julia for scientific computing'' for this paper?
  \item Restructure non-conservative stuff and add MHD benchmarks
  \item Add new features (Jesse's mesh and solver) to the list and update version, numer of examples, features, \etc
  \item Shall we re-create the schematic overview in tikz?
  \item Shall we compare \trixi to other open source frameworks such as MFEM, NGSolve, DealII, DUNE, FENICS, Firedrake, ClawPack, ...?
  \item Are there other aspects we should discuss?
\end{itemize}
\begin{quote}
  Compared to an extended abstract, a full paper presents more of the background
  and context motivating the work. It compares the work to other approaches taken
  in the field and gives some additional insights on the conference contribution.
  Use cases back up the work by showing how it can be used.
\end{quote}}
